TBD

### 2020-11-03 outputs/paper/paper.Rmd
Added citations

## Figure 4
```{r}
acs <- read_dta("post_strat_data-2.dta")
acs <- labelled::to_factor(acs)
incomeinfoacs <- acs %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
incomegraphacs <- incomeinfoacs %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "ACS Distribution of Household Income", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))

@@

## Figure 5
```{r}
ageinfoacs <- acs %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
agegraphacs <- ageinfoacs %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "ACS Distribution of Respondent Age", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))

@@

## Figure 6
```{r}
raceinfoacs <- acs %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
racegraphacs <- raceinfoacs %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "ACS Distribution of Respondent Race", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))

@@

## Table 6
```{r}
Table6 <- post_strat_cellcount_2 %>% 
  dplyr::select(
    age_group, race_ethnicity, household_income_grouped, n, prop
  ) %>% 
  head() %>% 
  kable(align = "c",
        format = "simple",
        col.names = c("Age Group", "Race", "Household Income", "Number of Repondents", "Proportion of Responses"),
        digits = 6
        ) 
Table6
```

@@

```{r include=FALSE}
aggregate(tbdata[8], list(tbdata$race_ethnicity), mean)

```

@@

# References

>>>>

## Figure 4
```{r}
# read in data
acs <- read_dta("post_strat_data-2.dta")
# label the data as it is a dta
acs <- labelled::to_factor(acs)
#create a tibble that includes counts and proportions based on groups
incomeinfoacs <- acs %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
#Graph this tibble in a pie graph
incomegraphacs <- incomeinfoacs %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "ACS Distribution of Household Income", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))

@@

## Figure 5
```{r}
#create a tibble that includes counts and proportions based on groups
ageinfoacs <- acs %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
#Graph this tibble
agegraphacs <- ageinfoacs %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "ACS Distribution of Respondent Age", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))

@@

## Figure 6
```{r}
#create a tibble that includes counts and proportions based on groups
raceinfoacs <- acs %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
#Graph this tibble in a pie graph
racegraphacs <- raceinfoacs %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "ACS Distribution of Respondent Race", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))

@@

## Table 6
```{r}
#Generate a table that displays the first couple responses from the cell count that was generated for weighting 
Table6 <- post_strat_cellcount_2 %>% 
  dplyr::select(
    age_group, race_ethnicity, household_income_grouped, n, prop
  ) %>% 
  head() %>% 
  kable(align = "c",
        format = "simple",
        col.names = c("Age Group", "Race", "Household Income", "Number of Repondents", "Proportion of Responses"),
        digits = 6
        ) 
Table6
```

@@

```{r include=FALSE}
#Get general percentage of people voting for Trump by Race
aggregate(tbdata[8], list(tbdata$race_ethnicity), mean)
#get overal percentage of people voting for Trump
mean(tbdata$binary)  
```

@@

# References
- R Core Team (2020). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna,
  Austria. URL https://www.R-project.org/.
- Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686
- Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2020). dplyr: A Grammar of Data Manipulation. R package version
  1.0.2. https://CRAN.R-project.org/package=dplyr
- Douglas Bates, Martin Maechler, Ben Bolker, Steve Walker (2015). Fitting Linear Mixed-Effects Models Using lme4. Journal of
  Statistical Software, 67(1), 1-48. doi:10.18637/jss.v067.i01.
- Jared E. Knowles and Carl Frederick (2020). merTools: Tools for Analyzing Mixed Effect Regression Models. R package version 0.5.2.
  https://CRAN.R-project.org/package=merTools
- Hadley Wickham, Jim Hester and Romain Francois (2018). readr: Read Rectangular Text Data. R package version 1.3.1.
  https://CRAN.R-project.org/package=readr
- Yihui Xie (2020). knitr: A General-Purpose Package for Dynamic Report Generation in R. R package version 1.29.
- Yihui Xie (2015) Dynamic Documents with R and knitr. 2nd edition. Chapman and Hall/CRC. ISBN 978-1498716963
- Yihui Xie (2014) knitr: A Comprehensive Tool for Reproducible Research in R. In Victoria Stodden, Friedrich Leisch and Roger D.
  Peng, editors, Implementing Reproducible Computational Research. Chapman and Hall/CRC. ISBN 978-1466561595
- Hadley Wickham and Evan Miller (2020). haven: Import and Export 'SPSS', 'Stata' and 'SAS' Files. R package version 2.3.1.
  https://CRAN.R-project.org/package=haven
- JJ Allaire and Yihui Xie and Jonathan McPherson and Javier Luraschi and Kevin Ushey and Aron Atkins and Hadley Wickham and Joe Cheng
  and Winston Chang and Richard Iannone (2020). rmarkdown: Dynamic Documents for R. R package version 2.3. URL
  https://rmarkdown.rstudio.com.
- Yihui Xie and J.J. Allaire and Garrett Grolemund (2018). R Markdown: The Definitive Guide. Chapman and Hall/CRC. ISBN 9781138359338.
  URL https://bookdown.org/yihui/rmarkdown.
- Monica Alexander. (2019, September 07). Analyzing name changes after marriage using a non-representative survey. Retrieved from https://www.monicaalexander.com/posts/2019-08-07-mrp/
- The New York Times. (n.d.). 2016 Presidential Election Results: Donald J. Trump Wins. Retrieved from https://www.nytimes.com/elections/2016/results/president
- US Census Bureau. (2020, October 16). Population. Retrieved from https://www.census.gov/topics/population.html
- NCSL. (2020). The Electoral College. Retrieved from https://www.ncsl.org/research/elections-and-campaigns/the-electoral-college.aspx
- Financial Times. (2020, October 30). Biden vs Trump: US presidential election poll tracker. Retrieved from https://ig.ft.com/us-election-2020/
- Survey Systems (2020). “Sample Size Calculator.” Sample Size Calculator - Confidence Level, Confidence Interval, Sample Size, Population Size, Relevant Population - Creative Research Systems, 2020, www.surveysystem.com/sscalc.htm.
- Amy Sorkin, John Cassidy, & Jonathan Blitzer. (2018). Donald Trump Compounds His "Shithole Countries" Bigotry with Lies. Retrieved from https://www.newyorker.com/news/daily-comment/donald-trump-compounds-his-shithole-countries-bigotry-with-lies
- Philip Bump. (2020, September 30). Analysis | Donald Trump doesn't really care about the white supremacist threat, and you're not going to make him. Retrieved from https://www.washingtonpost.com/politics/2020/09/30/donald-trump-doesnt-really-care-about-white-supremacy-youre-not-going-make-him/
- Kevin Liptak, & Kristen Holmes. (2020, July 01). Trump calls Black Lives Matter a 'symbol of hate' as he digs in on race. Retrieved from https://www.cnn.com/2020/07/01/politics/donald-trump-black-lives-matter-confederate-race/index.html
